---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

**NOTE: This is a toy package created for expository purposes. It is not meant to actually be useful. If you want a package for factor handling, please see [forcats](https://cran.r-project.org/package=forcats).**

### foofactors

Factors are a very useful type of variable in R, but they can also drive you nuts. This package provides some helper functions for the care and feeding of factors.

### Installation

```{r installation, eval = FALSE}
devtools::install_github("xinyaofan/foofactors")
```
  
### Quick demo

####Binding two factors via `fbind()`:

```{r}
library(foofactors)
library(forcats)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```
####freq_out() function
Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work. Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```

####detect factors that should be character 

We regard a factor is a true factor if  # unique values != length, otherwise it is a chracter. If we want to judge a factor is a true factor or a character,use our dec_fac() function to achieve this goal! 
```{r}
factor1<-factor(c("small","medium","big"))
factor2<- factor(c("1","2","2"))
```

We know factor1 is a character while factor2 is a really factor. 
```{r}
dect_fac(factor1)
dect_fac(factor2)
```

See, use our function can get the same result!
####reorder a factor in a descending order
In R, we have a function fct_rev() to reorder a factor. This can help us reorder a factor in a descending order. This is sometimes useful when plotting a factor
```{r}
x<-factor(c("1", "2", "3", "4"))
y<-factor(c("a","b","c","d"))
levels(fct_rev(x))
levels(fct_rev(y))
```
Use our reorder_des() function, you can get the same result!
```{r}
levels(reorder_desc(x))
levels(reorder_desc(y))
```
####sets levels to the order in which they appear in the data.
Sometimes, we want to get the levels of a factor and also keep their previous order in the factor.
```{r}
a<-factor(c("b","b","c","a"))
b<-factor(c("2","2","1","4"))
```
And we know the results should be "b","c","a" and "2","1","4". Now we can use our function to check the answers.
```{r}
levels(set_level(a))
levels(set_level(b))
```
See, the same answer as what we expect it to be.
